### 2019-08-09 ch2_dynbenchmark.tex
fix citations and remove bibliography at end of chapter

	\item \textbf{Component 1}: This method returns the first component of a principal component analysis (PCA) dimensionality reduction as a linear trajectory. This method is especially relevant as it has been used in a few studies already \cite{kouno_temporaldynamicstranscriptional_2013,zeng_pseudotemporalorderingsingle_2017}.

@@

The dyngen (\href{https://github.com/dynverse/dyngen}{https://github.com/dynverse/dyngen}) workflow to generate synthetic data is based on the well established workflow used in the evaluation of network inference methods \cite{schaffter_genenetweaversilicobenchmark_2011,marbach_wisdom_2012} and consists of four main steps: network generation, simulation, gold standard extraction and simulation of the scRNA-seq experiment. At every step, we tried to mirror real regulatory networks, while keeping the model simple and easily extendable. We simulated a total of 110 datasets, with 11 different topologies.

@@

One of the main processes involved in cellular dynamic processes is gene regulation, where regulatory cascades and feedback loops lead to progressive changes in expression and decision making. The exact way a cell chooses a certain path during its differentiation is still an active research field, although certain models have already emerged and been tested in vivo. One driver of bifurcation seems to be mutual antagonism, where genes \cite{xu_regulationbifurcatingcell_2015} strongly repress each other, forcing one of the two to become inactive \cite{graf_forcingcellschange_2009}. Such mutual antagonism can be modelled and simulated \cite{wang_quantifyingwaddingtonlandscape_2011,ferrell_bistabilitybifurcationswaddington_2012}. Although such a two-gene model is simple and elegant, the reality is frequently more complex, with multiple genes (grouped into modules) repressing each other \cite{yosef_dynamicregulatorynetwork_2013}.

@@

The importance of using multiple metrics to compare complex models has been stated repeatedly \cite{norel_selfassessmenttrap_2011}. Furthermore, a trajectory is a model with multiple layers of complexity, which calls for several metrics each assessing a different layer. We therefore defined several possible metrics for comparing trajectories, each investigating different layers. These are all discussed in Supplementary Note 1 along with examples and robustness analyses when appropriate.

@@

\clearpage

\clearpage
\section{References}
\printbibliography[heading=none]

>>>>

	\item \textbf{Component 1}: This method returns the first component of a principal component analysis (PCA) dimensionality reduction as a linear trajectory. This method is especially relevant as it has been used in a few studies already \cite{Kouno2013-km,zeng_pseudotemporalorderingsingle_2017}.

@@

The dyngen (\href{https://github.com/dynverse/dyngen}{https://github.com/dynverse/dyngen}) workflow to generate synthetic data is based on the well established workflow used in the evaluation of network inference methods \cite{schaffter2011,marbach_wisdom_2012} and consists of four main steps: network generation, simulation, gold standard extraction and simulation of the scRNA-seq experiment. At every step, we tried to mirror real regulatory networks, while keeping the model simple and easily extendable. We simulated a total of 110 datasets, with 11 different topologies.

@@

One of the main processes involved in cellular dynamic processes is gene regulation, where regulatory cascades and feedback loops lead to progressive changes in expression and decision making. The exact way a cell chooses a certain path during its differentiation is still an active research field, although certain models have already emerged and been tested in vivo. One driver of bifurcation seems to be mutual antagonism, where genes \cite{Xu2015-kn} strongly repress each other, forcing one of the two to become inactive \cite{graf_forcingcellschange_2009}. Such mutual antagonism can be modelled and simulated \cite{wang_quantifyingwaddingtonlandscape_2011,ferrell_bistabilitybifurcationswaddington_2012}. Although such a two-gene model is simple and elegant, the reality is frequently more complex, with multiple genes (grouped into modules) repressing each other \cite{Yosef2013-mj}.

@@

The importance of using multiple metrics to compare complex models has been stated repeatedly \cite{Norel2011}. Furthermore, a trajectory is a model with multiple layers of complexity, which calls for several metrics each assessing a different layer. We therefore defined several possible metrics for comparing trajectories, each investigating different layers. These are all discussed in Supplementary Note 1 along with examples and robustness analyses when appropriate.

@@
